The necessity of hypermedia RDF and an approach to achieve it

### 2012-03-01 eswc-2012/workshop2.tex
lod sparql bridge
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@140 43ef1190-90fd-4dd7-a769-d0121f02b80e

>>>>

\section{Bridging LOD and SPARQL}

In many cases, it is sufficient to get a small number of resources to
collect the data needed for a given usage, but slightly more involved
queries (e.g. ``what kind of connections exists between Kate Bush, Roy
Harper and bands that have sold more than 200 million albums?'') would
likely cause thousands of resources to be downloaded and examined. For
this, more advanced graph pattern matching as well as more advanced
mechanisms for source selection is
required. \cite{springerlink:10.1007/978-3-642-25073-6-38} provides
some techniques that should prove very valuable in this respect and so
it becomes important that SPARQL can be used with Linked Data in a
RESTful manner.

In the Linked Data Design
Issue\footnote{\url{http://www.w3.org/DesignIssues/LinkedData}} Tim
Berners-Lee notes ``To make the data be effectively linked, someone
who only has the URI of something must be able to find their way the
SPARQL endpoint.'', but this is generally not possible today without
requiring out-of-band information, which implies that non-REST
interactions are required.

The triples needed to do this is already defined in
VoID\footnote{\url{http://vocab.deri.ie/void}} and in use:
\begin{verbatim}
<> void:inDataset [ void:sparqlEndpoint </sparql> . ] .
\end{verbatim}
